% !TEX root = resume.tex

\newpage
\hugeBold{Greetings!}\\\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\\\\
I love a good challenge. Over the past seven years, I have developed my skills as a full-stack developer building scalable, highly available enterprise applications. Whether I'm fine-tuning responsive website components, designing new SQL relations, composing complex object-oriented hierarchies or learning entirely new languages, I am growth-driven and love picking up new skills and using code to solve problems.
\\\\
% I am as comfortable polishing up a UI interface as I am sleuthing through event logs and databases, and I find that cleaning up an old code base can be as rewarding as building a completely new feature.
% Working at ConsumerCellular I built and maintained ASP.NET RestAPIs with Vue.js and Razor for the front end with a few opportunities to incorporate GraphQL and Docker.
During my time at ConsumerCellular I built and maintained in-house enterprise software, supporting vital functions such as billing, collections and fraud prevention by translating extremely complex business rules into highly reliable, resilient and recoverable code. Early this year I joined StackOverflow with a mission to deliver the public Q\&A website to a high volume of consumers by optimizing our code to support thousands of requests per second, as well as creating experiments to quickly test and iterate on new feature ideas to increase engagement.
\\\\
Unfortunately my tenure at StackOverflow was brief -- in May I was part of the \href{https://stackoverflow.blog/2023/05/10/a-message-from-prashanth-chandrasekar-ceo-stack-overflow/}{30\% of the engineering team who was laid off} as the company reckoned with the stiff economic market and need to maintain profitability. Nonetheless I am extremely grateful for the opportunity to broaden my experience. Over the years, I have designed and lead development on new features and applications from the ground up and I look forward to applying what I've learned to new challenges.
\\\\
In addition to my technical knowledge, my prior experience in the service industry has equipped me with the soft skills necessary to adapt and flourish in any organization. I self-manage my own workload while supporting the larger team effort, striving to create a positive and supportive environment. I thoroughly enjoy planning and organization and am accountable for my actions while taking pride in the craft and thoughtfulness of my work.
\\\\
% In addition to my technical knowledge, my experience in the service industry has imbued me with skills critical to any organization. I adapt well to many different workflows and management styles, and I thrive on feedback and collaboration with my coworkers. I self-manage my own workload while supporting the larger team effort, striving to create a positive and productive environment. I thoroughly enjoy planning and organization and am accountable for my actions while taking pride in the craft and thoughtfulness of my work.
%REPLACE WITH SOMETHING BETTER
% My background as a craftsperson has taught me the value of quality in a competitive market. My time as a bike mechanic has shown me that I relish work that is challenging: replete with constantly evolving techniques and new systems to learn, while also fostering development and mastery of skills over time. When I worked as a barista I felt that every drink I poured was a reflection of myself -- I try to make every morsel of work my best.
I greatly appreciate your time spent reviewing my resume -- if you think my attitudes and talents could be a good fit, I would be delighted to be considered as an addition to the team!
\\\\\\

\rightAlignBold{Kind Regards,}
\rightAlignBold{Amanda Ryman}


